Optimal (Multiway) Spatial Joins

### 2024-06-01 5.1.tex
5.1

It remains to prove that no two distinct tuple $\bm{t}_1, \bm{t}_2$ will be mapped to the same tuple in $\J_2$. Assume,on the contrary, $\bm{t}_1, \bm{t}_2$ are mapped to the same tuple $\bm{t} \in \J_2$. Then, $\bm{t}_1[i] = \bm{t}[i] = \bm{t}_2[i]$ for $i\in [k-3]$ and $i = k-1$. Moreover, $\bm{t}_1[k-2]$ and $\bm{t}_2[k-2]$ are both trimmed segment of $\bm{t}[k-2]$. Since the trimmed segment is unique, $\bm{t}_1[k-2] = \bm{t}_2[k-2]$. Hence, $\bm{t}_1 = \bm{t}_2$, which contradicts the assumption.

>>>>

It remains to prove that no two distinct tuple $\bm{t}_1, \bm{t}_2$ will be mapped to the same tuple in $\J_2$. Assume, on the contrary, $\bm{t}_1, \bm{t}_2$ are mapped to the same tuple $\bm{t} \in \J_2$. Then, $\bm{t}_1[i] = \bm{t}[i] = \bm{t}_2[i]$ for each $i\in [k-3]$ and $i = k-1$. Moreover, $\bm{t}_1[k-2]$ and $\bm{t}_2[k-2]$ are both the trimmed segment of $\bm{t}[k-2]$. By the uniqueness of the trimmed segment, $\bm{t}_1[k-2] = \bm{t}_2[k-2]$. Hence, $\bm{t}_1 = \bm{t}_2$, which contradicts the assumption.

### 2024-06-01 5.2.tex

\noindent \underline{\em Proof of Statement (1).} Consider any tuple $\bm{t} = (r_1,...,r_{k-3}, h', v) \in \J(R_1,...,R_{k-3},H',V)$. Let $h$ be the full segment of $h'$. Since $\bm{t} \in \J(R_1,...,R_{k-3},H',V)$, $B_\bm{t}$, which is the intersection point of $h'$ and $v$, is in $r_i$ for $i \in [k-3]$. As $h$ is the full segment of $h'$, $B_\bm{t} \in h$. Since $v$ also contains $B_\bm{t}$, $B_\bm{t}$ is also the intersection of $h$ and $v$. Let $r_{k-2}$ be an arbitrary rectangle in $\contained_{R_{k-2}}(\bm{t})$. By the definition of $\contained_{R_{k-2}}(\bm{t})$, $r_{k-2}$ covers effective segment of $h'$, whose right enpoint is $B_{\bm{t}}$. Therefore, $B_{\bm{t}}$ is in $r_{i}$ for $i \in [k-2]$, and $\bm{t} \in \J(R_1,...,R_{k-2},H,V)$. Moreover, since the left endpoint of the effective segment of $h'$ is the same as the left endpoint of $h$, $r_{k-2}$ contains the left endpoint of $h$. Therefore, $\bm{t} \in \J_2$.

>>>>

\noindent \underline{\em Proof of Statement (1).} Consider any tuple $\bm{t} = (r_1,...,r_{k-3}, h', v) \in \J(R_1,...,R_{k-3},H',V)$. Let $h$ be the full segment of $h'$. Folloing our conventions, $B_\bm{t}$ denotes the intersection point of $h'$ and $v$, and it is covered by the rectangles $r_1,...,r_{k-3}$. As $h$ is the full segment of $h'$, $B_\bm{t} \in h$, and $B_\bm{t}$ is also the intersection of $h$ and $v$. Let $r_{k-2}$ be an arbitrary rectangle in $\contained_{R_{k-2}}(\bm{t})$. By the definition of $\contained_{R_{k-2}}(\bm{t})$, $r_{k-2}$ covers the effective segment of $h'$, whose right enpoint is $B_{\bm{t}}$. Therefore, $B_{\bm{t}}$ is in $r_{i}$ for $i \in [k-2]$. Equivalently, $h \cap v \bigcap_{i = 1}^{k-2} r_i = B_\bm{t} \neq \emptyset$. Hence,
$\bm{t} \in \J(R_1,...,R_{k-2},H,V)$. Moreover, since $r_{k-2}$ covers the effective segment of $h'$, whose left endpoint is the same as the left endpoint of $h'$ and $h$, $r_{k-2}$ also covers the left endpoint of $h$. Therefore, $\bm{t} \in \J_2$.
